Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-25 manuscript/climate_sensitivity_draft.Rmd
minor change from Norm
update author contributions

### Author Contribution 
KAT, IM, and AJT designed the research. Tree-ring chronologies were developed by RH under guidance of AJT and NP. Trait data were collected by IM, JZ under guidance of NK and LS. Other plot data were collected by IM, AS, EGA, and NB under guidance of EGA and WM. Data analyses were performed by IM under guidance of KAT and VH. KAT and IM interpreted the results. IM and KAT wrote the first draft of manuscript, and all authors contributed to revisions.

>>>>

### Author Contribution 
KAT, IM, and AJT designed the research. Tree-ring chronologies were developed by RH under guidance of AJT, KAT, and NP. Trait data were collected by IM and JZ under guidance of NK, KAT, and LS. Other plot data were collected by NB in coordination with WM and by IM and AS under guidance of EGA and KAT. Data analyses were performed by IM under guidance of KAT and VH. KAT and IM interpreted the results. IM and KAT wrote the first draft of manuscript, and all authors contributed to revisions.
